---
title: '"PSY 8712 Week 8 Project"'
author: "Minjeong Seo"
date: "`r Sys.Date()`"
output: 
  html_document:
    df_print: paged
---

# **Reproducible Image and Online Resources**
An image of this project as of *"`r Sys.Date()`"* can be accessed by [clicking this link](https://mybinder.org/v2/gh/min9509/psy8712-week8/HEAD).
An interactive web app is available by [clicking this link instead](add shiny app).

# **Script Settings and Resources**
I used message to suppress all output from a chunk but display a copy of the executed code. Just because message suppress any informational messages.
```{r setup, message=FALSE}
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
library(tidyverse)
```

# ***Data Import and Cleaning**

```{r import date}
week8_tbl <- read_csv("../data/week3.csv") %>%
  mutate(q5 = 6 - q5) %>%
  mutate(timeStart = ymd_hms(timeStart)) %>%
  mutate(timeEnd = ymd_hms(timeEnd)) %>%
  mutate(condition = factor(condition, levels = c("A", "B", "C"), labels = c("Block A", "Block B", "Control"))) %>%
  mutate(gender = factor(gender, levels = c("M", "F"), labels = c("Male", "Female")))  
```