---
title: '"PSY 8712 Week 8 Project"'
author: "Minjeong Seo"
date: "`r Sys.Date()`"
output: 
  html_document:
    df_print: paged
---

# **Reproducible Image and Online Resources**
An image of this project as of *"`r Sys.Date()`"* can be accessed by [clicking this link](https://mybinder.org/v2/gh/min9509/psy8712-week8/HEAD).
An interactive web app is available by [clicking this link instead](https://min9509.shinyapps.io/shiny_week8/).

# **Script Settings and Resources**
I used message to suppress all output from a chunk but display a copy of the executed code. Just because message suppress any informational messages.
```{r setup, message=FALSE}
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
library(tidyverse)
```

# **Data Import and Cleaning**
This chunk is for importing and cleaning data. I used read_csv to import data, mutate to change data types, and rowwise with mutate and mean to prepare section 4.
```{r import date}
week8_tbl <- read_csv("../data/week3.csv") %>%
  mutate(q5 = 6 - q5) %>%
  mutate(timeStart = ymd_hms(timeStart)) %>%
  mutate(timeEnd = ymd_hms(timeEnd)) %>%
  mutate(condition = factor(condition, levels = c("A", "B", "C"), labels = c("Block A", "Block B", "Control"))) %>%
  mutate(gender = factor(gender, levels = c("M", "F"), labels = c("Male", "Female"))) %>%
  rowwise() %>%
  mutate(meanQ1_6 = mean(c(q1, q2, q3, q4, q5, q6))) %>%
  mutate(meanQ8_10 = mean(c(q8, q9, q10))) 
```

# **Visualization**
This chunk is for visualizing the table (Q1~Q6) and the scatter plot (mean Q1-Q6 and mean Q8-Q10) with the OLS regression line. To visualize the table and plot, I used the select function with df_print in the YAML and ggplot with geom_point(to make the scatter plot) and geom_smooth(to add OLS regression line) .
```{r visualization}
week8_tbl %>%
  select(q1:q6)

week8_tbl %>%
  ggplot(aes(x = meanQ1_6, y = meanQ8_10)) +
  geom_point() +
  geom_smooth(method = "lm", color = "purple") +
  labs(x = "Average scores of Q1 ~ Q6", y = "Average scores of Q8 ~ Q10")
```

# **Analysis**
This chunk is used to obtain the correlation between mean Q1-Q6 and mean Q8-Q10. I observed a correlation of `r format(round(cor(week8_tbl$meanQ1_6, week8_tbl$meanQ8_10), 2), nsmall = 0)`, but the p-value is 0.56, which means it is not significant.
```{r analysis}
cor.test(week8_tbl$meanQ1_6, week8_tbl$meanQ8_10)
```

# **Data Export**
This chunk is used to export data. 
```{r export}
week8_tbl %>% 
  saveRDS(file = "../shiny_week8/week8_data.rds")
```
